Data analytics effects in Baseball

### 2023-10-30 manuscription/manuscription.tex
draft1

\section{Introduction}
\label{sec:intro}
Sport psychology, an interdisciplinary field integrating concepts from both psychology and sports science, has become a fundamental element in enhancing athletic performance across a spectrum of sports, baseball included.
Its primary focus is to comprehend and optimize the psychological components that affect an athlete's mindset, emotions, and conduct, ultimately aiming to elevate their performance.
Now, let's explore specific key domains within sport psychology that exert significant influence on baseball players.
Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field. 
Previous studies in the field \cite{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.

@@

% roadmap
The rest of the paper is organized as follows.\\
The data will be presented in Section~\ref{sec:data}.\\
The methods are described in Section~\ref{sec:meth}.\\
The results are reported in Section~\ref{sec:resu}.\\
A discussion concludes in Section~\ref{sec:disc}.\\

@@

\section{Discussion}
\label{sec:disc}

\begin{thebibliography}{9}

  \bibliography{refs.bib}
  \bibliographystyle{chicago}
\end{thebibliography}

>>>>

\section{Introduction}
\label{sec:intro}
Sport psychology, an interdisciplinary field integrating concepts from both psychology and sports science, has become a fundamental element in enhancing athletic performance across a spectrum of sports, baseball included.
Its primary focus is to comprehend and optimize the psychological components that affect an athlete's mindset, emotions, and conduct, ultimately aiming to elevate their performance.
Now, let's explore specific key domains within sport psychology that exert significant influence on baseball players.
Baseball was selected as the focal sport due to its comprehensive nature, allowing for an analysis of nearly every facet of the game, except for the mental readiness of the player upon entering the field. 
Previous studies in the field \cite*{Dalmass2018baseball} have provided valuable insights, and we seek to build upon their findings.

@@

% roadmap
The rest of the paper is organized as follows.\\
The data will be presented in Section~\ref{sec:data}.\\
The methods are described in Section~\ref{sec:meth}.\\
The results are reported in Section~\ref{sec:resu}.\\

@@

The study involved recruiting 26 members from the baseball team. Among these participants, 0.385, were pitchers, 0.423 were infielders, and 0.192 were outfielders. 
Splitting these groups, half of the pitchers were in the control group, while the remaining half were in the experimental group. For the infielders, 
0.455 were in the control group, and 0.545 were in the experimental group. As for the outfielders, 0.4 were in the control group, and 0.6 were in the experimental group.
Due to limitations in the sample size—considered small—the study's reliability may have been affected since it was conducted as a convenience sample. 
While the recruitment method was straightforward as it targeted the university's varsity team, the size of the sample could potentially impact the study's outcomes. 
Notably, the study would have ideally required a minimum sample size of 128, calculated using a specific formula considering an alpha level of .05, t-tests for independent groups, 
an effect size of 0.5, and a power of 0.8. Implementing this study on a larger scale, such as within a Minor League Baseball organization, 
would have made achieving the required sample size more feasible.

\bibliographystyle{chicago} % We choose the "plain" reference style
\bibliography{refs} % Entries are in the refs.bib file
